---
title: "Problem 3 Week 02"
format: pdf
embed-resources: true
toc: true
--- 

# Problem 3

R packages often come with internal datasets, that are typically used for use in the help documentation examples. These can be accessed through the use of the system.file() function. See an example below.

system.file("extdata", package = "FlowSOM")

Using what we have learned about file.path navigation, search your way down the file.directory of the FlowSOM and flowWorkspace packages, and identify any .fcs files that are present for use in the documentation.

# FlowSom package file directory 

```{r}
system.file("extdata", package = "FlowSOM")
list.files();

```

```{r}
system.file("extdata", package = "FlowSOM")
```

```{r}
system.file("extdata", package = "flowWorkspace")
```

```{r}
list.files(path = "C:/Users/lynnm/AppData/Local/Programs/R/R-4.5.2/library/FlowSOM/extdata", pattern = ".fcs", full.names = FALSE, recursive = FALSE)
```

```{r}
list.files(path = "C:/Users/lynnm/AppData/Local/Programs/R/R-4.5.2/library/flowWorkspace/extdata", pattern = ".fcs", full.names = FALSE, recursive = FALSE)
```